\subsection{\cite{kharytonava2012word,kharytonava2012taming}}

Kharytonava inspects SA in Turkish specifically for noun compounds. The SA that is observed in Kharytonava's examples are rather different in what is left after SA. For a beginning consider the noun compounds in (\ref{compound}).

\begin{exe}
    \ex \label{compound}
    \begin{xlist}
        \ex \gll
        \textit{Anne-m} \textit{not} \textit{defter-i-ni} \textit{yıka-mış.} \\ mother-{\First}{\Sg} note book-{\Third}{\Sg}.{\Poss}-{\Acc} wash-{\Prf}[{\Third}{\Sg}] \\
        \glt `It seems like my mother washed the notebook'
        
        \ex \gll 
        \textit{Anne-m} \textit{not} \textit{defter-im-i} \textit{yıka-mış} \\ mother-{\First}{\Sg} note book-{\First}{\Sg}.{\Poss}-{\Acc} wash-{\Prf}[{\Third}{\Sg}] \\
    \end{xlist}
\end{exe}

When no possessor is present for the compound, the default agreement marker is third person singular in Turkish. This changes when the compound is used in possessive. The different behaviour of SA that Kharytonava presents comes into play exactly in this change. When a noun compound is used in conjunction SA can take two shapes as in (\ref{compoundSA}).

\begin{exe}
    \ex \label{compoundSA}
    \begin{xlist}
        \exi{No SA}
        \ex
        \gll 
        \textit{doğum} \textit{yer-in} \textit{ve} \textit{tarih-iniz} \\ birth place-{\Second}{\Sg} {\And} date-{\Second}{\Pl} \\
        \glt ${}$
        
        \exi{Full SA}
        \ex \label{compoundSAb}
        \gll 
        \textit{doğum} \textit{yer} \textit{ve} \textit{tarih-iniz} \\ birth place {\And} date-{\Second}{\Pl} \\
        \glt ${}$
        \exi{Partial SA} 
        \ex \label{compoundSAc}
        \gll
        \textit{doğum} \textit{yer-i} \textit{ve} \textit{tarih-iniz} \\ birth place-{\Third}{\Sg} {\And} date-{\Second}{\Pl} \\
        \glt `Your birthplace and birthdate'
    \end{xlist}
    ${}$ \hfill Adapted from \cite{kharytonava2012taming}
\end{exe}

The possessive marker is suspended in (\ref{compoundSAb}) and there is no remnant of agreement whereas in (\ref{compoundSAc}) leaves behind a possessor that is third person, yet the interpretation of possessive for the second conjunct is still in the second person singular. On the surface the existence of a third person possessor after SA for a second person possessor seems problematic. Kharytonava addresses this not as a structural sharing or deletion analysis, she rather uses Impoverishment and Feature Geometry to explain such a configuration of SA. She indicates that features are monovalent for referring expressions and exponent insertion is modulated by Subset Principle following DM. I reiterate her feature geometry for Turkish Referring Expression (in this case possessor) with the corresponding exponents in Table \ref{tab:kharyfeatures}
\begin{table}[hbt!]
    \caption{Feature Geometry of {\Poss} in Turkish}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
         \multicolumn{2}{|c|}{Features} & \multirow{2}{*}{Exponent}  \\ \cline{1-2}
         Participant & Individuation  & \\ \hline
         Speaker & $\emptyset$ & \textit{-Im} \\ \hline 
         Addressee & $\emptyset$ & \textit{-In} \\ \hline 
         Speaker & Group & \textit{-ImIz} \\ \hline 
         Addressee & Group & \textit{-InIz} \\ \hline 
         $\emptyset$ & $\emptyset$ & \textit{-(s)I(n)} \\ \hline 
         $\emptyset$ & Group & \textit{-lArI} \\ \hline 
    \end{tabular}
    \label{tab:kharyfeatures}
\end{table}

Now the SA in noun compounds works by deletion of features. See the feature templatic view of no SA in (\ref{compoundSA}) below.

\begin{itemize}
    \item $\alpha$-\textsc{Addressee}-\textsc{Group} {\And} $\beta$-{\textsc{Addressee}-\textsc{Group}}
\end{itemize}

The feature set for \textsc{Addressee}-\textsc{Group} is by Subset Principle, is \textit{-InIz}. On this templatic view in the first conjunct we delete the features instead of the exponent itself. This feature deletion results in the following templatic view and the exponent \textit{-(s)I(n)} is inserted after the first conjunct.

\begin{itemize}
    \item $\alpha$-$\emptyset$-$\emptyset$ {\And} $\beta$-{\textsc{Addressee}-\textsc{Group}}
\end{itemize}

Further on this point \cite{kharytonava2012word} shows that Turkish speakers prefer the Partial SA in (\ref{compoundSA}) to the full SA. It is also my judgments to be so. Since third person singular agreement on verbal and nominal predicate domain is not expressed by an overt phonological exponent, SA in instances like (\ref{impoverished}) might also be considered as a deletion of the referential expression marker alongside the tense.

\begin{exe}
    \ex \label{impoverished}
    \begin{xlist}
        \ex \gll 
        \textit{Ben} \textit{hasta} \textit{ve} \textit{yorgun-du-m.} \\ {\First}{\Sg}[{\Nom}] sick[{\Third}{\Sg}] {\And} tired-{\Pst}-{\First}{\Sg} \\
        \glt `I was sick and tired'
        
        \ex \gll
        \textit{Ben} \textit{ev-e} \textit{gid-ecek} \textit{ve} \textit{gel-ecek-ti-m.} \\ {\First}{\Sg}[{\Nom}] house-{\Dat} come-{\Fut}[{\Third}{\Sg}] {\And} come-{\Fut}-{\Pst}-{\First}{\Sg} \\
        \glt `I was going to come home and go'
    \end{xlist}
\end{exe}

This type of analysis for SA falls under an ellipsis like analysis operation on morphemes as features. Which has more appeal and makes predictions about SA in noun compounds.