\subsection{\cite{kornfilt2012revisiting}} \label{kornfilt}
Kornfilt reiterates points in \cite{kornfilt1996some}. Mainly that SA is a syntactic operation much like gapping or ellipsis, that can only target syntactic categories, and she gives her account of RNR (Right Node Raising) to account for SA. She claims that a suffix can be suspended only if it has a syntactic projection. In this way she predicts to posit functional heads like Num (NumP), Case (KP), and Possession (PossP) since all three can have SA distinctly. Figure \ref{fig:kornfilt} illustrates the abstract RNR analysis for the examples of SA in (\ref{heads}).
\begin{exe}
    \ex \label{heads}
    \begin{xlist}
        \ex \label{heads1} SA of {\Pl}\\*
        \gll Kitap ve defter-ler \\ 
        book {\And} notebook-{\Pl} \\
        \glt Reading1: `Books and notebooks' \\*
        Reading2: `A book and notebooks'
        
        \ex \label{heads2} SA of {\Acc}\\*
        \gll Kitap ve defter-i al-dı-m. \\ 
        book {\And} notebook-{\Acc} buy-{\Pst}-{\Fsg} \\
        \glt `I bought the book and the notebook.'
        
        \ex SA of {\Poss}\\*
        \gll Kitap ve defter-im nerede? \\ 
        book {\And} notebook-{\Poss}.{\Fsg} where \\
        \glt Reading1: `Where is the book and my notebook?' \\* 
        Reading2: `Where is my book and notebook?'
    \end{xlist}
\end{exe}


\begin{figure}[hbt!]
    \centering
    \begin{forest}
        [ConjP, s sep=30mm
            [Conj' 
                [XP$_1$ 
                    [YP]
                    [X$_1$, name=x1]]
                [Conj]
                [XP$_2$ 
                    [YP]
                    [X$_2$, name=x2]]]
            [X, name=x3]]
\draw[rounded corners=1em, ->] (x1.south) -- ++(south:2em) -| (x3.south);
\draw[rounded corners=1em, ->] (x2.south) -- ++(south:1em) -| (x3.south);
    \end{forest}
    \caption{RNR proposal for SA}
    \label{fig:kornfilt}
\end{figure}

This analysis is also the same analysis that Kornfilt provides for backwards ellipsis for a sentence like (\ref{backwardellipsis}) as in Figure \ref{fig:backwardellipsis}. This way Kornfilt regards SA as another ellipsis process operating on projection heads instead of phrases.

\begin{exe}
    \ex \label{backwardellipsis}
    \gll Ahmet al-dı ve Mehmet sat-tı kitab-ı. \\ 
    A[{\Nom}] buy-{\Pst}[{\Tsg}] {\And} M[{\Nom}] sell-{\Pst}[{\Tsg}] book-{\Acc} \\
    \glt `Ahmet bought and Mehmet sold the book.'
\end{exe}

\begin{figure}[hbt!]
    \centering
    \begin{forest}
        [ConjP, s sep=30mm 
            [Conj' 
                [TP 
                    [DP\\\textit{Ahmet}]
                    [\ldots 
                        [\sout{DP}, name=tk]
                        [V\\\textit{al}]]]
                [Conj\\\textit{ve}]
                [TP 
                    [DP\\\textit{Mehmet}]
                    [\ldots 
                        [\sout{DP}, name=tl]
                        [V\\\textit{sat}]]]]
            [DP\\\textit{kitab-ı}, name=DP]]
\draw[rounded corners=1em, ->] (tk.south) -- ++(south:2.5em) -| (DP.south);
\draw[rounded corners=1em, ->] (tl.south) -- ++(south:1.5em) -| (DP.south);
    \end{forest}
    \caption{RNR analysis for Backward Ellipsis}
    \label{fig:backwardellipsis}
\end{figure}

Kornfilt argues against SA of derivational suffixes because an example like (\ref{kornfiltder}) has a fixed order of conjuncts for a successful suspension. This makes a clear distinction for what is possible to suspend and what is not. 

\begin{exe}
    \ex \label{kornfiltder}
    \begin{xlist}
        \ex \gll [tuz ve limon]-luk \\ salt {\And} lemon-{\Der} \\ 
        \glt `[salt and lemon] shaker'
        
        \ex \gll *[limon ve tuz]-luk \\ lemon {\And} salt-{\Der} \\
        \glt `[lemon] and [saltshaker]'
    \end{xlist}
\end{exe}

The proposed analysis of Kornfilt does not explain why SA of {\Poss} is ungrammatical in a string of {\Pl-\Poss}. As a terminal node in syntax, there is nothing preventing SA of {\Poss} in {\Pl-\Poss} by the RNR analysis. It also does not predict why SA of {\Pl-\Poss} is ambiguous, but SA of {\Case} is not as shown in (\ref{optionalornot}).

\begin{exe}
    \ex \label{optionalornot} 
    \begin{xlist}
        \ex Ambiguous SA of {\Pl}\\* 
        \gll kitap ve kalem-ler \\ book {\And} pencil-{\Pl} \\
        \glt SA: `books and pencils' \\*
        No SA: `a book and pencils'
        
        \ex Ambiguous SA of {\Poss}\\* 
        \gll kitap ve kalem-im \\ book {\And} pencil-{\Poss}.{\Fsg} \\
        \glt SA: `my book and my pencil' \\*
        \glt No SA: `a book and my pencil'
        
        \ex Unambiguous SA of {\Acc}\\*
        \gll kitap ve kalem-i al-dı-m. \\ book {\And} pencil-{\Acc} take-{\Pst}-{\Fsg} \\
        \glt SA: `I took the book and the pencil' \\*
        No SA: `* I took a book and the pencil'
    \end{xlist}
\end{exe}

