\chapter{\MakeUppercase{conclusion}}

In this thesis my primary aim was to investigate the interactions and core workings of SA. I used empirical and theoretical devices to better represent SA and its relations. I did not have a small and fixed set of problems for which I engage in finding solutions. The topic itself on the other hand is very specific and the number of languages it is observed in is few. I realized that the literature has fixated on only the suspended part and not the environment. That is why my primary objective became pinpointing the space that SA occupies in Turkish. I investigated the type of morphemes that can take part in SA, the environment SA is used in and what it can bring for a study of sentence processing in Turkish. Answers to the questions in (\ref{questions}) can be found in my thesis, in the order they are presented:

\begin{exe}
\ex \label{questions}
\begin{xlisti}
    \ex What are the analyses for SA in Turkish, and similar processes in other languages?: Some form of sharing for Turkish is prominent, ellipsis in other languages like German, Mari, Ossetic, and Korean.
    \ex What type of affixes can be targeted by SA?: Mostly inflectional, relative frequency of a suffix increases acceptability.
    \ex Does the type of conjoiner have an effect in performing SA?: \textit{veya} `or' lowers acceptability in the nominal domain and focus clitics hinder SA.
    \ex Does SA create environments for testing notions like Reanalysis?: Yes, it results in participants preferring structurally simpler constructions over a morphologically complex operation like SA.
    \ex How does an informed analysis of SA look like? Constraints for RNR analysis or a morphology specific deletion analysis.
    \ex Is SA beyond a morphological word possible?: Yes, if the vocabulary insertion for the conjoiner is changed from a free form conjoiner \textit{ve} `and' to a suffix \textit{-(y)Ip}.  
\end{xlisti}
\end{exe}

My observations indicate that SA in Turkish is highly reserved for inflectional suffixes. It is not necessarily hard to process. Other than its main function, it can be used to create structural ambiguities that lead to increased processing difficulty with disambiguations that contradict it. It can also cause lasting effects even after reading the sentence is completed. SA is a process of ellipsis that target terminal nodes instead of individual morphemes. SA being optional or successful is dependent on its environment, which is conjunction. The suffix \textit{-(y)Ip} can be considered as an example for SA beyond a morphological word although it is not typically warranted. In the following sections, I propose some empirical considerations that could be used to further investigate the claims I made, or the points that arise from the experiments I conducted.


\section{Pragmatics and Suspended Affixation}

In the experiments and the descriptions provided for SA, it is not clear what function it serves. There is no prominent reading differences resulting from performing or not performing SA. One point is the question of why \textit{veya} `or' reduces acceptability for SA of {\Acc}. The analysis I provided focuses on the interaction between the use of a conjoiner and pragmatics. It suggests the reading of `$\wedge$' (and) to be present. This can not be achieved by \textit{veya} `or' because in the environment I used, it interacted with pragmatics and lost the reading of \textit{ve} `and'. A further research into this point can be made by using \textit{veya} `or' in different environments like conditionals, quantificational determiners, and questions. This means that the environment of SA is placed under another environment and the argument I make can be further investigated.

\section{Why use only two conjuncts?}

In the beginning of my thesis, I asserted that SA is possible with more than two conjuncts, but the literature revolves around two conjuncts. According to my observations, SA of derivational suffixes is not viable and SA does not have too much processing cost. Yet I made these observations using only two conjuncts for the environment of SA. The same points need to be tested with increased number of conjunctions. Examples for SA of derivational suffixes can be found in a corpus, yet these examples usually involve more than two conjuncts. SA may be used as a strategy to avoid repetition of derivational suffixes. That is why those examples are found in the corpus. The processing cost is low, maybe because the process of retrieving the suffix and implementing it for only one conjunct is not labor intensive for an increase in processing difficulty. These are some of the points that makes it worth looking into SA with numerous conjuncts.


\section{Why diverge on both empirical and theoretical grounds?}

In my thesis I make use of both the empirical and theoretical tools to provide an argument or support a point. In issues that are novel and oriented towards answering a question, I used empirical tools. They provide me with how a variable interacts with a process that I am after and how it can be explained. A simple yes and no session with myself as a native Turkish speaker was not enough to capture the fine points. These can be related to the effect of a conjoiner change, the effects of incremental changes in suspension, and many more. I used theoretical grounds to argue for or against a formal analysis provided for SA, and how to characterize a clitic \textit{ile/=lA} or a suffix \textit{-(y)Ip}. 

\section{My experience in writing a thesis}

Throughout the process of writing my thesis, I tried to compartmentalize my tasks. The nature of my thesis and my goal of majorly exploring SA made it more suitable for such a way of studying. I was able to make myself engage with my thesis in different ways and shed different lights on the problems. I like to think I was consistent with what I produced in the time period I had. I decided what topic to study early on, and to my surprise it bore fruit and offered an array of different aspects that I can approach piece by piece. My thesis is not a single line going from one dot to the other. I like to think of it as the collection of the concentric circles around SA and what they interact with. 
