\chapter{\MakeUppercase{structure of suspended affixation}}


In this chapter, I present my analyses for SA. I use the inferences I have drawn from the empirical results and the theoretical considerations as well as my own native judgments. These analyses include a consideration for the exact machinery of performing SA. I later present theoretical analyses for the suffixes \textit{ile/=(y)lA} and \textit{-(y)Ip} and how they relate to SA.

\input{sections/sa-analysis}

\input{sections/whyconjoinerile.tex}

\input{sections/whyconjoiner-Ip.tex}

% \input{sections/whynotRNR.tex}

\section{Conclusion for the structure of suspended affixation}

The following points make up a general summary of the theoretical consideration that are made in this chapter. They are based on how morphemes are treated in the deletion process and how the environment is analyzed. 

\begin{itemize}
    \item The structural interpretation of SA requires adjustments to the existing analyses provided for ellipsis (e.g. RNR) or a new one that solely operates for the morphological deletion process. Addressing the morphemes for a movement, or deletion is the key to structurally representing SA.
    
    \item SA in the conjunction of headless relative clauses show that it is performed before a full linear order of morphemes is formed.
    
    \item The interpretation of the SA environment and the properties that surround the vocabulary insertion of the clitic conjoiner \textit{ile/=lA} require taking an operation like Impoverishment into account.
    
    \item The constructions formed with \textit{-(y)Ip} show that SA can be performed even though what is left is not a morphological word. The morphological word constraint for SA can be explained by a selection of vocabulary item for insertion of the conjoiner instead of hindering SA altogether. A morphological word requires the insertion of a free form \textit{ve} `and' and a non-morphological word requires the insertion of \textit{-(y)Ip}. 
    
    \item SA can not be performed on focused arguments as the alternative question clitic \textit{=mI} and the focus clitic \textit{=dA} hinder suspension.
\end{itemize}


