\chapter{\MakeUppercase{literature survey}} \label{litsurvey}


\cite{geoffrey1967turkish} is credited with the term SA and first observations of it in Turkish. A closer look in the literature written in Turkish reveals that the phenomenon is observed and even addressed before \citep{emre1945turk,gencan1966dilbilgisi}.

\citet[par 219]{emre1945turk} observes that copular forms of \textit{-DI} and \textit{-mIş} can be suspended together with the agreement markers. He does not recognize the sole suspendability of the agreement markers. One difference in his observation is that not performing suspended affixation is interpreted as an emphasis on the conjuncts. This is a point which has not been raised since in the literature of SA, the effect of SA in interpretation. He does not provide examples of SA in the nominal domain. \citet[par 382]{gencan1966dilbilgisi} gives similar examples of SA in the verbal domain, however he includes examples of SA in the nominal domain and almost all possible suffixes are represented. He claims that performing SA creates discrepancies in the sentence so avoiding them makes the contrasts in a sentence more apparent.  

Categorized as an agglutinating language with many inflectional and derivational functions represented mostly by distinct morphemes, Turkish has many affixes that can be suspended, both in nominal and verbal domains. Some articles that exclusively examine SA in Turkish are: \cite{orgun1995flat}, \cite{kabak2007turkish}, \cite{broadwell2008turkish}, \cite{kornfilt2012revisiting}, \cite{kharytonava2012word,kharytonava2012taming}, and \cite{akkucs2016suspended}.

Some other articles investigating SA in other languages are: \cite{erschler2012suspended}, and \cite{erschler2018suspended} for Ossetic, \cite{yoon2017lexical} for Korean, \cite{despic2017suspended} for Serbian, \cite{guseva2017postsyntactic} for Mari, and \cite{pounder2006broken} for German. These articles range from giving the relative data and its limitations to the structural accounts and predictions for SA. In this chapter I first summarise the literature regarding SA in Turkish, later I summarise the literature regarding SA in other languages. I finish the chapter by providing some accounts for conjunctions.


\section{Suspended affixation in Turkish}

\input{sections/orgun.tex}

\input{sections/kabak.tex}

\input{sections/broadwell.tex}

\input{sections/kornfilt.tex}

\input{sections/kharytonava.tex}

\input{sections/akkus.tex}

\input{sections/interim-summary.tex}


\section{Suspended affixation in other languages}

The focus and effort of this study is limited to SA in Turkish, but it is beneficial to take observations from other languages where similar SA-like phenomena exist. In the following subsections I provide summaries of such articles in a chronological order. \cite{pounder2006broken} shows examples of SA and conjunction reduction from German, \cite{guseva2017postsyntactic} shows examples of SA from Mari, \cite{despic2017suspended} shows an example of a certain Serbian clitic that mimics SA-like behaviour, \cite{yoon2017lexical} shows examples from Korean, and \cite{erschler2012suspended,erschler2018suspended} show examples from Ossetic.

\input{sections/pounder.tex}

\input{sections/guseva.tex}

\input{sections/despic.tex}

\input{sections/yoon.tex}

\input{sections/erschler.tex}

\input{sections/summary.tex}

The environment of SA is conjunction. I give what conjunction analysis I follow and what the constraints are in forming conjunctions in the following section.

\input{sections/conjunction}