\chapter{\MakeUppercase{testing suspended affixation}} \label{sec:testing}


In this chapter my aim is to explore some aspects of SA empirically. These include the suspendability of derivational suffixes, the processing cost of SA, and the effect of the conjoiner. I present 2 experiments I conducted. The first is an acceptability study with 214 participants that investigates the suspendability of derivational suffixes with two conjoiners. The second is a self-paced reading study with 160 participants that investigates the processing cost of SA with different number of suffixes and two different conjoiners.


\input{experiments/acceptability/report/EXP1report-knitr}

\input{experiments/selfpaced/report/EXP2report-knitr}

\section{Conclusion of Experiments 1 and 2}

The first experiment was conducted in the nominal domain and the analyses were based on responses. It aimed to compare suspendability of derivational suffixes to the suspension of inflectional {\Acc}. The results and the analyses indicate that suspendability of derivational suffixes is less related to structural explanations than it is to the frequency of those suffixes. This does not mean, however, that a structural explanation is not required. If the context relative frequency of a suffix is given as an explanation, a more gradient measurement is needed. Additionally using a conjoiner \textit{veya} `or' decreased acceptability of SA overall, this needs to be addressed theoretically. I reserve the discussion of the conjoiner to Chapter 5.


The second experiment was conducted in the verbal domain and the analyses were made based on the reading times. It aimed at observing the effects of performing SA. It compared suspending different number of suffixes with using two different conjoiners for the environment. It made another comparison using contrasting features in the first conjunct to distinguish an effect of SA from an effect of feature mismatch between the conjuncts. The results and the analyses indicate that performing SA is costly but not additive. The cost of performing SA is different than an effect of mismatching features between the conjuncts. 









