\chapter*{\MakeUppercase{acknowledgement}}

Language is in the epicenter of human interaction and it is a marvel of human cognitive capability. My main strife is understanding others, and embrace my place among them. I am glad that I chose linguistics as a scholarly career. 

I wholeheartedly thank my advisor Prof. Aslı Göksel first, as she had all the patience during the courses I took, and all the wisdom that I inquired for. It is no small feat to have a nod of approval or an appraisal from her. It is a sobering feedback and encouragement that one can receive when listening to her. She appreciates humor like no other and is not afraid of cracking a smile when the joke merits one. I was fortunate to be her student. 

I am thrilled to thank Assist. Prof. Pavel Loga\v{c}ev. He introduced me to a whole new realm of linguistics where quantified observations and methodology is of essence. He is one great person who makes satire during a conversation without you knowing it. It makes it all the funnier and enjoyable once you figure it out. I appreciate that he took both the time and the effort to extend my critical thinking beyond the borders I knew existed.

I would like to extend my gratitude and thanks to Prof. Balkız Öztürk. Thanks to her, I was able to take part in a TUBITAK (Turkish National Institute of Science and Technology) funded project (No:117E971) together with Prof. Tunga Güngör and Assoc. Prof. Arzucan Özgür, Utku Türk, and others. This project enabled me to focus on my work by helping with my financial security and to contribute to the resources for the study of Turkish. I also thank Assoc. Prof Elena Guerzoni, Prof. Meltem Kelepir, Assoc. Prof. Didar Akar, Prof. A. Sumru Özsoy, and Prof. Erguvanlı Taylan for never leaving a question on the air, providing crucial feedback and help locate wisdom in linguistics.

I sincerely thank my peers. They provided a healthy and constructive space of competition where supporting each other lead to the betterment of our work and collectively bound us together with happy and fond memories. I would like to thank Hande, Semra, Demet, Utku, Furkan, and Noyan for the conversations we had, for the work we have done, and for the times we shared together. I only feel like living when my voice is heard so thanks for listening to me. 

I am a man of many words with shaky cohesion and difficult to follow points, but I wanted this piece of acknowledgement to be an exception. I try to be a good person and remembered as one, nothing more. I plan on doing right by the time I was spared, and it is only just to do so.
